ASYMPTOTIC VALIDITY OF A FULLY SEQUENTIAL ELIMINATION PROCEDURE FOR INDIFFERENCE-ZONE RANKING AND SELECTION WITH TIGHT BOUNDS ON PROBABILITY OF CORRECT SELECTION

### 2015-05-06 paper/wish/wsc15paper.tex
5-5-155-5-155-5-155-5-155-5-15

{\it PF: I stopped here.}
We are doing all this because we want to see that $f\left(\mathcal{C}\left(\delta,\cdot\right),\delta\right)$
looks like the right or wrong selection decision of an algorithm that
depends on a standard Brownian motion instead of $\mathcal{C}\left(\delta,\cdot\right)$,
and this will give us the proof because we will be able to use the
theory developed by Frazier (2014) to prove the theorem. Thus, the
following step is to find the limit of $q_{tx}^{F,\delta}\left(A\right)$
when $\delta$ goes to zero, which is called $q_{tx}^{F}\left(A\right)$
and equal to

@@

@@

By the comments given at the beginning of this section, we know that
we can work with the algorithm defined by

@@

Now, we define
\begin{eqnarray*}
\hat{\tau}_{n+1}\left(\delta\right) & = & \mbox{inf}\left\{ t\in\left\{ \tau_{n}\delta^{2},\left(\tau_{n}+1\right)\delta^{2},\ldots\right\} :\mbox{ min}_{x\in A_{n}}q_{t/\delta^{2},x}^{'}\left(A_{n}\right)\leq c\mbox{ or }\mbox{max}_{x\in A_{n}}q_{t/\delta^{2},x}^{'}\left(A_{n}\right)\geq P_{n}\right\} 
\end{eqnarray*}
We denote the corresponding continuous hitting times by $\left(\tau_{n}\left(\delta\right)\right)_{n}$,
which are defined as

@@

Using that $\mathcal{C}\left(\delta,\cdot\right)$ is right-continuous,
we can prove that $\hat{\tau}_{n}\left(\delta\right)-\tau_{n}\left(\delta\right)\rightarrow0$
with probability $1$ as $\delta\rightarrow0$, and so we can use
$\mathcal{C}\left(\delta,\tau_{n}\left(\delta\right)\right)$ instead
of $\mathcal{C}\left(\delta,\hat{\tau}_{n}\left(\delta\right)\right)$
in the limit.

@@

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.4\textwidth}
        \centering
        \includegraphics[width=\textwidth]{plot5}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.4\textwidth}
        \centering
        \includegraphics[width=\textwidth]{plot6}
    \end{subfigure}
    \caption{Known variances and $P^*=0.9$. $\lambda_{100}=1,\lambda_{99}=1+\frac{(0.5)(98)}{99},\cdots,\lambda_{1}=0.5,n_{0}=0$.
    In this example, our theorem is true: the IZ guarantee is always satisfied and the inequality is tight as $\delta$ goes to zero.
    \label{fig: tahi3}}
\end{figure}

@@

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.4\textwidth}
        \centering
        \includegraphics[width=\textwidth]{plot3}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.4\textwidth}
        \centering
        \includegraphics[width=\textwidth]{plot4}
    \end{subfigure}
    \caption{Unknown variances and $P^*=0.9$. $\lambda_{100}=10\sqrt(2),\lambda_{99}=10+\frac{(10)(98)}{99}(\sqrt(2)-1),\cdots,\lambda_{1}=10,n_{0}=15$.
    In this example, our theorem is true: the IZ guarantee is satisfied and the inequality is tight as delta goes to zero. If we want that the IZ guarantee be 
    satisfied in all the cases, we can just increment $n_{0}$.
    \label{fig: tahi2}}
\end{figure}

@@

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.4\textwidth}
        \centering
        \includegraphics[width=\textwidth]{plot1}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.4\textwidth}
        \centering
        \includegraphics[width=\textwidth]{plot2}
    \end{subfigure}
    \caption{Known variances, $P^*=0.9$, $\lambda_{100}=10,\lambda_{99}=\cdots=\lambda_{1}=1,n_{0}=0$. This was a hard example to find
    and it was specially chosen to ilustrate our theorem. In practice, we would choose $n_{0}>0$ and the IZ guarantee will be satisfied. \label{fig: tahi}}
\end{figure}

>>>>

{\it PF: I stopped here.}
%We are doing all this because we want to see that $f\left(\mathcal{C}\left(\delta,\cdot\right),\delta\right)$
%looks like the right or wrong selection decision of an algorithm that
%depends on a standard Brownian motion instead of $\mathcal{C}\left(\delta,\cdot\right)$,
%and this will give us the proof because we will be able to use the
%theory developed by Frazier (2014) to prove the theorem. Thus, the
The following step is to find the limit of $q_{tx}^{F,\delta}\left(A\right)$
when $\delta$ goes to zero, which is called $q_{tx}^{F}\left(A\right)$
and equal to

@@

\subsection{The Main Result}

@@

By the comments given at the beginning of this section, we know that
we can work with the algorithm, which we call the discrete-time BIZ algorithm, defined by

@@

Now, we define
\begin{eqnarray*}
\hat{\tau}_{n+1}\left(\delta\right) & = & \mbox{inf}\left\{ t\in\left\{ \tau_{n}\delta^{2},\left(\tau_{n}+1\right)\delta^{2},\ldots\right\} :\mbox{ min}_{x\in A_{n}}q_{t/\delta^{2},x}^{'}\left(A_{n}\right)\leq c\mbox{ or }\mbox{max}_{x\in A_{n}}q_{t/\delta^{2},x}^{'}\left(A_{n}\right)\geq P_{n}\right\} 
\end{eqnarray*}
The corresponding BIZ algorithm is called the continuous-time BIZ algorithm. We denote the corresponding continuous hitting times by $\left(\tau_{n}\left(\delta\right)\right)_{n}$,
which are defined as

@@

Using that $\mathcal{C}\left(\delta,\cdot\right)$ is right-continuous,
we can prove that the difference of the probability of correct selection of the discrete-time BIZ algorithm and the  probability of correct selection of the continuous-time BIZ algorithm converge to zero as $\delta$ goes to zero. Then we can use the continuous-time BIZ algorithm in the limit, i.e. we can use $\mathcal{C}\left(\delta,\tau_{n}\left(\delta\right)\right)$ instead
of $\mathcal{C}\left(\delta,\hat{\tau}_{n}\left(\delta\right)\right)$. (The details may be found in a full version which will be submitted soon to arXiv).

@@

\begin{figure}[h]
  \centering
   \begin{subfigure}[b]{0.4\textwidth}
      \centering
       \includegraphics[width=0.7\textwidth]{plot5}
    \caption{Known variances and $P^*=0.9$. In this example, our theorem is true: the IZ guarantee is always satisfied and the inequality is tight as $\delta$ goes to zero.
    \label{fig: tahi3}}
   \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.4\textwidth}
        \centering
         \includegraphics[width=0.7\textwidth]{plot3}
             \caption{Unknown variances and $P^*=0.9$. In this example, our theorem is true: the IZ guarantee is satisfied and the inequality is tight as delta goes to zero. If we want that the IZ guarantee be 
    satisfied in all the cases, we can just increment $n_{0}$.
    \label{fig: tahi2}}
    \end{subfigure}
        \hfill
    \begin{subfigure}[b]{0.4\textwidth}
        \centering
         \includegraphics[width=0.7\textwidth]{plot1}
    \caption{Known variances, $P^*=0.9$ This was a hard example to find and it was specially chosen to ilustrate our theorem. In practice, we would choose $n_{0}>0$ and the IZ guarantee will be satisfied. \label{fig: tahi}}
    \end{subfigure}
    \caption{PCS for different numerical experiments
\label{fig:tahi10}}

\end{figure}

@@

@@
